---
title: "Predator Filter Code"
author: "Colby Hause"
date: "June 26, 2018"
output: html_document
---

Use this code to specify the amount of upstream movement considered as "predation" and then filter out those detections. min_distance_rkm is the distance you set for the removal of detections: any fish that has moved that value or more upstream will be removed from data set

(This is the exact same Rmd located in the 2017 analysis folder on the share drive)

```{r}
upriver_movement_jsats <- function(all_detections, df_taglist, min_distance_km, low_rkm = 0, high_rkm = 550) {
  #edit_detections <- subset(all_detections, rkm > low_rkm & rkm < high_rkm)   #use this line if using rkm
  edit_detections <- subset(all_detections, Genrkm > low_rkm & Genrkm < high_rkm)  #use this line if using Genrkm
  all_tags <- unique(df_taglist$Hex)
  df_removed_detections <- NULL
  count <- 1
  num_tags <- length(unique(df_taglist$Hex))
  for (tag in all_tags) {
    print(paste(count, "/", num_tags))
    ind_tag <- subset(edit_detections, edit_detections$Hex == tag)
    ind_tag <- ind_tag[order(ind_tag$dtf), ]
    all_rows <- c(1:nrow(ind_tag))
    sliding_low <- high_rkm
    if (nrow(ind_tag) > 0 ) {  
      for (row in all_rows) {
        #first_rkm <- ind_tag$rkm[row] use this if using regular rkm
        first_rkm <- ind_tag$Genrkm[row]
        #second_rkm <- ind_tag$rkm[row + 1] use this if using regular rkm
        second_rkm <- ind_tag$Genrkm[row + 1]
        first_date <- ind_tag$dtf[row]
        second_date <- ind_tag$dtf[row + 1]
        if (row == nrow(ind_tag)) { #Ends the loop once it gets to the end of the data.frame without throwing an error.
          break
        }
        if (second_rkm < first_rkm & second_rkm < sliding_low) { #Reassign the points that are your limit
          sliding_low <- second_rkm
        }
        if (second_rkm == sliding_low) {
          low_date <- second_date
        }
        if (second_rkm - sliding_low > min_distance_km) {
          final_date <- low_date
          removed_detections <- ind_tag[(ind_tag$dtf > low_date), ] #This needs to be added to new data.frame for ALL tags.
          df_removed_detections = rbind(df_removed_detections, removed_detections)
          all_detections <- all_detections[!(all_detections$Hex == tag & all_detections$dtf > final_date), ] #Keeps last detection before moving upstream
          sliding_low <- high_rkm
          break
        }
      }
    }
    count <- count + 1
  }
  write.csv(df_removed_detections, "Removed Detections from Upstream Movement.csv")
  return(all_detections)
}

```

Code to run through: use your original group dataframes 
```{r}
# first get your split up groups from waterfall plot code:
#allgroups <- read.csv( "file path of where your [year]AllFishGroups is")

#group1 <- allgroups %>% 
  #filter(Rel_group == "2017_SJ_SCARF1" | Rel_group == "2017_SJ_SIRF1" )

#group2 <- allgroups %>% 
  #filter(Rel_group == "2017_SJ_SCARF2" | Rel_group == "2017_SJ_SIRF2" )

#example:
#new_group1 <- upriver_movement_jsats(group1, group1, 12)
#new_group2 <- upriver_movement_jsats(group2, group2, 12)

```

